Coherent optical association of a single molecule

### 2020-10-23 paper.tex
Inset for Fig 2C
Update plot using new molecular lifetime measurement

\begin{figure*}[t!]
  \includegraphics[width=\textwidth]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.204(13) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure*}

@@

Guided by coupled channel calculations,
we locate the Raman resonance for the atom to molecule transition at
$770.59430(17) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state will be detected as loss of atoms
in the post experiment image when compared to the initial image.
We observed a Fourier limited linewidth which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B) without turning on the second frequency. The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$. The molecule we form has a lifetime of $0.204(13) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

@@

>>>>

\begin{figure*}[t!]
  \includegraphics[width=\textwidth]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure*}

@@

Guided by coupled channel calculations,
we locate the Raman resonance for the atom to molecule transition at
$770.571504(85) ~\mathrm{MHz}$ (Fig.~\ref{f-lifetime}A)
with a $15 ~\mathrm{mW}$ tweezer at $288560 ~\mathrm{GHz}$
which corresponds to a $145 ~\mathrm{GHz}$ single photon detuning.
% (We can maybe add information about the prediction here?)
%% Prediction
% This excited state used in the Raman transition was measured in our previous experiment using photoassociation to be at $288560 GHz$ from our atomic state. The ground molecular state has not been observed previously in experimentally. Based on our measurement of FB resonance, interaction shift and the binding energy of the 4422 bound state. Theory prediction was at $770.1 MHz$. \todo{more, mention/cite Jeremy}
% The background level of $31\%$ corresponds to the probability of preparing the two atoms in the relative motional ground state.
% When the atoms are transferred into the molecule state by the Raman transition, there is a decrease in the two body survival since the resulting molecule is dark to our imaging sequence. % directly detected by our imaging step.
The molecular state is dark to the imaging step,
so successful transfer of the atoms to the molecular state will be detected as loss of atoms
in the post experiment image when compared to the initial image.
We observed a Fourier limited linewidth which is evidence of a coherent transfer.
In order to verify the coherence of the transfer directly,
we fix the two photon detuning on resonance and scan the pulse time.
Fig.~\ref{f-raman}C shows the observed Rabi oscillation between the atomic and molecular states.
Fitting the data with a decaying Rabi oscillation suggests that
$69\%$ of initial ground state atoms are transferred into the molecular state.

In order to understand the fidelity of molecule formation, we fit our measurements to a model that includes a Raman Rabi frequency and a finite lifetime for the molecular state (Fig.~\ref{f-lifetime}A). We account for the effect of atomic state loss by measuring the single and two body lifetime of the atoms directly (Fig.~\ref{f-lifetime}B) without turning on the second frequency. The fit shows that we have a Raman Rabi frequency of $2\pi\times3.282(42) ~\mathrm{kHz}$. The molecule we form has a lifetime of $0.1990(90) ~\mathrm{ms}$ which is the main limitation on the fidelity of the transfer. The molecule lifetime can be measured directly by preparing the molecule with a $\pi $ pulse and then using a second $\pi $ pulse to dissociate the molecule back to atoms after a variable wait time (Fig.~\ref{f-lifetime}C). The result shows a molecular lifetime consistent with our fitting of the decaying Rabi oscillation.

@@

% Shift figure 4 x axis
% Try to move 3C forward
% Inset in 4AB
% Inset in 2C (3A) (or as a separate figure)
% Maybe remove 3A (move into supplemental material)
% Arrow head for molecule overlaps the datapoint
% 4C as inset to 2B
